Using Personal Activity Diaries to Enhance Electronic Health Records

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
highres

We posit that significant gains in patient-clinician communications can be made by helping clinicians to better understand a patient's life between their visits to the doctor. In this paper, we propose a mechanism for augmenting electronic health records with \emph{personal activity diaries}, high resolution records of a patient's daily life, derived automatically from personal activity sensors.  These activity diaries establish a shared context for discussing the patient's lifestyle and condition.

>>>>

We posit that significant gains in patient-clinician communications can be made by helping clinicians to better understand a patient's life between their visits to the doctor. In this paper, we propose a mechanism for augmenting electronic health records with \emph{personal activity diaries}, high-resolution records of a patient's daily life, derived automatically from personal activity sensors.  These activity diaries establish a shared context for discussing the patient's lifestyle and condition.
